Enforced Invariant Confluence

### 2018-04-19 doc/paper/sections/related_work.tex
Progress on related work.

\paragraph{Super relevant stuf}
% Super relevant
% Towards Fast Invariant Preservation in Geo-replicated Systems
% title={Coordination avoidance in database systems},
% title={Putting consistency back into eventual consistency},
% title={The homeostasis protocol: Avoiding transaction coordination through program analysis},
% title={Automating the choice of consistency levels in replicated systems},
% title={Making geo-replicated systems fast as possible, consistent when necessary},
% title={'Cause I'm strong enough: Reasoning about consistency choices in distributed systems},
% Feral
% The CISE Tool: Proving Weakly-Consistent Applications Correct
% Declarative Programming over Eventually Consistent Data Stores
% Extending Eventually Consistent Cloud Databases for Enforcing Numeric Invariants

@@

\paragraph{CALM Theorem}
\cite{alvaro2013declarative}
\cite{ameloot2013relational}
\cite{ameloot2016weaker}
\cite{hellerstein2010declarative}
\cite{alvaro2011dedalus}
\cite{alvaro2010boom}
\cite{alvaro2011consistency}
\cite{conway2012logic}
\cite{zinn2012win}

\paragraph{CRDTs}
% coordination free convergence as opposed to coordination free invs describe inv-confluence as sort of a crdt with certain properties or something.

>>>>

\newcommand{\sieve}{\textsc{sieve}}
\paragraph{RedBlue Consistency and \sieve}
RedBlue consistency is a form of consistency that sits between causal
consistency and linearizability~\cite{li2012making}. With RedBlue consistency,
every operation is labelled as red or blue. All operations are executed with
causal consistency, but with the added restrictions that red operations are
executed in a single total order embedded within the causal ordering.
RedBlue consistency is similar to segmented invariant-confluence with a single
segment in which all red operations are removed from the segment's set of
allowable transactions.  In~\cite{li2012making}, Li et al.\ define
\defword{invariant safety} as a sufficient condition for RedBlue consistent
objects to be invariant-confluent.  Invariant safety is an analog of
invariant-closure for an operation-based (as opposed-to state
based~\cite{shapiro2011conflict}) system model.  In~\cite{li2014automating}, Li
et al.\ develop techniques to identify which operations are invariant safe.
Like invariant-closure, invariant safety is a sufficient but not necessary
condition for invariant-confluence. Li et al.\ develop sophisticated techniques
for deciding invariant safety that involve calculating weakest preconditions.
These techniques are complementary to our work and can be used to improve the
invariant-closure subroutine used by our decision procedures.

\paragraph{Super relevant stuf}

% Super relevant
% title={'Cause I'm strong enough: Reasoning about consistency choices in distributed systems},

% escrow

% Towards Fast Invariant Preservation in Geo-replicated Systems
% title={Coordination avoidance in database systems},
% title={Putting consistency back into eventual consistency},
% title={The homeostasis protocol: Avoiding transaction coordination through program analysis},
% title={'Cause I'm strong enough: Reasoning about consistency choices in distributed systems},
% Feral
% The CISE Tool: Proving Weakly-Consistent Applications Correct
% Declarative Programming over Eventually Consistent Data Stores
% Extending Eventually Consistent Cloud Databases for Enforcing Numeric Invariants

@@

\paragraph{CRDTs}
CRDTs~\cite{shapiro2011conflict, shapiro2011comprehensive} are distributed
semilattices with inflationary update methods. Due to their algebraic
properties, CRDTs can be replicated with strong eventual consistency without
the need for any coordination. Our definition of distributed objects and our
invariant-confluence system model are inspired directly by the corresponding
definitions and system models in~\cite{shapiro2011conflict}. Note that an
invariant-confluent object does not necessarily have to be eventually
consistent. In fact, equipping a distributed object with the trivial merge
function $x \join y = x$ makes the object invariant-confluent with respect
any set of transactions and any invariant, but it makes the object very
inconsistent. Thus, it's natural (though not necessary) to use CRDTs as
invariant-confluent distributed objects, achieving a combination of eventual
consistency and invariant-preservation. Our criteria in
\thmref{LatticeProperty} also borrow ideas from CRDTs, exploiting the nice
algebraic properties of semilattices.

\paragraph{CALM Theorem}
Bloom~\cite{alvaro2010boom, alvaro2011consistency, conway2012logic} and its
formalism, Dedalus~\cite{alvaro2011dedalus, alvaro2013declarative}, are
declarative Datalog-based programming languages that are designed to program
distributed systems. The accompanying CALM
theorem~\cite{hellerstein2010declarative, ameloot2013relational} states that if
a program can be written in the monotone fragment of these languages, then
there exists a coordination-free implementation of the program. Moreover,
monotone programs are invariant to message reordering, whereas non-monotone
programs may experience anomalies if messages are reordered in the network. The
CALM theorem provides guarantees about the outputs of a program, but it does
not guarantee that invariants are maintained throughout the duration of an
execution. Moreover, Bloom and Dedalus are general purpose programming
languages that can be used to implement a variety of distributed systems (e.g.
a sharded database), while invariant-confluence is defined strictly in the
context of replicated data.

\paragraph{Proof Assistants}
Our interactive decision procedure bears resemblance to interactive proof
assistants like Coq~\cite{coq2017}, Isabelle~\cite{nipkow2002isabelle},
Agda~\cite{norell2008dependently}, and Idris~\cite{brady2013idris}. Proof
assistants guide users through the process of interactively provided a proof
that witnesses the validity of a formula. Our interactive decision procedure
guides users through the process of interactively generating a set of reachable
and unreachable points that witness the invariant-confluence of an object. An
interesting avenue for future work is to integrate an proof assistant into our
interactive decision procedure. For example, a proof assistant could verify
that a state labelled unreachable by a user is actually unreachable.
